---
title: "CSViewer"
author: "Martin Frigaard"
output: 
  flexdashboard::flex_dashboard:

runtime: shiny
---

```{r setup, include=FALSE}
library(tidyverse)
library(inspectdf)
library(flexdashboard)
library(visdat)
library(shiny)
library(hrbrthemes)
library(data.table)
library(listviewer)
library(repurrrsive)
library(jsonlite)
library(htmlwidgets)
library(reactable)
library(DT)
library(polished)

# set theme for graphs from hrbrthemes
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc(
  base_family = "Ubuntu",
  strip_text_family = "TitilliumWeb-Regular",
  axis_title_family = "TitilliumWeb-Regular",
  subtitle_family = "TitilliumWeb-Regular",
  plot_title_family = "JosefinSans-Regular"
))
```


Sidebar {.sidebar}
=====================================

This dashboard allows you to upload a .csv data set and view it's contents in a variety of ways. 

Scroll through each page to see what your data looks like!

```{r fileInput-checkboxInput-radioButtons-radioButtons}
shiny::fileInput(inputId = "csvfiledata",
          label = "Upload CSV file",
          accept = c("text/csv",
                         "text/comma-separated-values,text/plain",
                         ".csv"))

shiny::checkboxInput(inputId = "header", label = "Header", value = TRUE)
```

Read more: 

1. [`reactable`](https://glin.github.io/reactable/) 
2. [`inspectdf`](https://alastairrushworth.github.io/inspectdf/) 
3. [`flexdashboard`](https://rmarkdown.rstudio.com/flexdashboard/)
4. [`listviewer`](https://github.com/timelyportfolio/listviewer)

Your data {data-orientation=rows}
=======================================================================

### View your data in a table (`reactable::reactable`)

```{r render-reactable}
renderReactable({
   reactable(dataReact1(), wrap = FALSE, resizable = TRUE, filterable = TRUE, 
             highlight = TRUE, height = 600)
  })
```

Memory Usage {data-orientation=rows}
=======================================================================

Row
-----------------------------------------------------------------------

```{r dataReact1}
dataReact1 <- reactive({
  
    req(input$csvfiledata)
  
        tryCatch(
      {
        
        df <- data.table::fread(input$csvfiledata$datapath, 
                                header = input$header, 
                                sep = ",", 
                                data.table = FALSE)
        
      },
      
      error = function(e) {
        
        # return a safeError if a parsing error occurs
        
        stop(safeError(e))
        
      }
      
    )
  
  })

```

### Memory usage (`inspectdf::inspect_mem`)

```{r render-inspect_mem}
shiny::renderPlot({
  dataReact1() %>% 
  inspectdf::inspect_mem() %>% 
  inspectdf::show_plot(text_labels = TRUE)
})
```


Missing Values {data-orientation=rows}
=======================================================================

Row
-----------------------------------------------------------------------

```{r dataReact2}
dataReact2 <- reactive({
    req(input$csvfiledata)
        tryCatch(
      {
        
        df <- data.table::fread(input$csvfiledata$datapath, 
                                header = input$header, 
                                sep = ",", 
                                data.table = FALSE)
      },
      error = function(e) {
        # return a safeError if a parsing error occurs
        stop(safeError(e))
      }
    )
  })

```

### Missing data (`inspectdf::inspect_na`)

```{r render-inspect_na}
shiny::renderPlot({
  dataReact2() %>% 
  inspectdf::inspect_na() %>% 
  inspectdf::show_plot(text_labels = TRUE)
})
```

### Missing data by type (`visdat::vis_dat`) 

```{r render-vis_dat}
shiny::renderPlot({
  dataReact2() %>% 
  visdat::vis_dat() + 
  coord_flip()
})
```

Numerical Variables {data-orientation=rows}
=======================================================================

Row
-----------------------------------------------------------------------

```{r dataReact3}
dataReact3 <- reactive({
    req(input$csvfiledata)
        tryCatch(
      {
        
        df <- data.table::fread(input$csvfiledata$datapath, 
                                header = input$header, 
                                sep = ",", 
                                data.table = FALSE)
        # numeric only
        df <- df %>% select_if(is.numeric)
      },
      error = function(e) {
        # return a safeError if a parsing error occurs
        stop(safeError(e))
      }
    )
  })
```


### Numerical variables (`inspectdf::inspect_num`)

```{r render-num_plot}
shiny::renderPlot({
  dataReact3() %>% 
  inspectdf::inspect_num() %>% 
  inspectdf::show_plot(text_labels = TRUE)
})
```


Correlations {data-orientation=rows}
=======================================================================

Row
-----------------------------------------------------------------------

### Correlations (`inspectdf::inspect_cor`) 

```{r render-cor_plot}
shiny::renderPlot({
  dataReact3() %>% 
  inspectdf::inspect_cor() %>% 
  inspectdf::show_plot(text_labels = TRUE)
})
```


Categorical Variables {data-orientation=rows}
=======================================================================


Row
-----------------------------------------------------------------------

```{r dataReact4}
dataReact4 <- reactive({
    req(input$csvfiledata)
  
    tryCatch(
      {
        
        df <- data.table::fread(input$csvfiledata$datapath, 
                                header = input$header, 
                                sep = ",", 
                                data.table = FALSE)
        # character vars 
        
        df <- df %>% 
          dplyr::select_if(is.character)
      },
      error = function(e) {
        # return a safeError if a parsing error occurs
        stop(safeError(e))
      }
    )
    
  })
```

### Categorical variables (`inspectdf::inspect_cat`)

```{r render-cat_plot}
shiny::renderPlot({
  dataReact4() %>% 
  inspectdf::inspect_cat() %>% 
  inspectdf::show_plot(text_labels = TRUE)
})
```

Imbalances {data-orientation=rows}
=======================================================================


Row
-----------------------------------------------------------------------

### Imbalances between categories  (`inspectdf::inspect_imb`)

```{r render-imb_plot}
shiny::renderPlot({
  dataReact4() %>% 
  inspectdf::inspect_imb() %>% 
  inspectdf::show_plot(text_labels = TRUE)
})
```


Sample data {data-orientation=rows}
=======================================================================

Row {data-height=100}
-----------------------------------------------------------------------

```{r includeMarkdown}
shiny::includeMarkdown(path = "sampledatainfo.md")
```

Row {data-height=900}
-----------------------------------------------------------------------

```{r downloadButton, message=FALSE, warning=FALSE}
splitLayout(cellWidths = c("22%", "78%"),
            wellPanel(
              downloadButton(outputId = "downloadData", 
               label = "Download a sample data:")),
              reactableOutput("OrigData"))

output$downloadData <- downloadHandler(
    filename = function() {
      paste("Sample", "Data", "Set", ".csv", sep = "")
    },
    content = function(file) {
      file.copy("SampleDataSet.csv", file)
    },
    contentType = "text/csv"
)
# read in the dataset
SampleDataSet <- readr::read_csv(file = "SampleDataSet.csv")

output$OrigData <- renderReactable({
    reactable(SampleDataSet, 
              resizable = TRUE, showPageSizeOptions = TRUE, 
              selection = "multiple", onClick = "select")
  })
```

BONUS: View lists! {data-orientation=rows}
=======================================================================

Row
-----------------------------------------------------------------------

### View JSON data  (`listviewer::jsonedit`)


```{r json}
# https://github.com/timelyportfolio/listviewer/issues/26
json <- jsonlite::fromJSON(got_chars_json(), simplifyDataFrame = FALSE)
renderJsonedit({
    listviewer::jsonedit(as.list(json)
      ,"change" = htmlwidgets::JS('function(){
        console.log( event.currentTarget.parentNode.editor.get() )
      }')
    )
})
```

